Cover Letter

### 2023-10-22 manuscript.qmd
Update

Asmaa Fahmy Kasem^1^, Hamdy Bakry Alqenawy^1^ ^\*^, Marwa Abd Elmawla Elgendi^1^, Radwa Rasheedy^1^, Rania Gamal^1^, Yasser M. Elrefaey^1^, Rowyna Hany Mohamed El Helw^1^, Rania Hassan Mostafa Ahmed^1^, Mohammad Nahel Sorour^1^, Mohamed Sameh Elsewefy^1^, Maya M. Abdelrazek^1^, Mohamed Yasser Galal Albahaie^1^, Khadiga Mostafa Hussein Hegab^1^, Mohamed Hamed Salama^1^, Ashraf Fawzy Nabhan^1^

@@

We acknowledge the effort and the spirit of goodwill of xx for their contribution to this work.

>>>>

Asmaa Fahmy Kasem^1^, Hamdy Bakry Alqenawy^1^ ^\*^, Marwa Abd Elmawla Elgendi^1^, Radwa Rasheedy^1^,  Rania Hassan Mostafa Ahmed^1^, Mohammad Nahel Sorour^1^, Mohamed Yasser Galal Albahaie^1^, Khadiga Mostafa Hussein Hegab^1^, Rania Gamal^1^, Yasser M. Elrefaey^1^, Rowyna Hany Mohamed El Helw^1^, Mohamed Sameh Elsewefy^1^, Maya M. Abdelrazek^1^, Mohamed Hamed Salama^1^, Ashraf Fawzy Nabhan^1^

@@

We acknowledge the contribution and the spirit of goodwill of Dr. Maha Khalifa, the healthcare advocate for her valuable insights.
